---
title: "API setups and results for some public classifiers and taggers of unstructured text data"
author: "Alireza Ahadi"
date: "`r Sys.Date()`"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# 1. Text analytics use cases

## 1.1 Sentiment analysis using uClassifer

**uClassifier** <https://www.uclassify.com/> is a free machine learning web service where you can easily create and use text classifiers. Here is the code to perform sentiment analysis on a given text data, in this case simply a string: 


```{r pressure}
library(tidyverse)

uClassifyURL = function(key, classifierName, text) {
    text = gsub(" ", "+", text)
    url = sprintf("https://api.uclassify.com/v1/uClassify/%s/classify/?readKey=%s&text=%s", classifierName, key, text)
    return(url)
  }
  
text = "I'm positive that my job search will lead me to the job that I truly deserve."
url = uClassifyURL('iGwAytFWYvvZ', 'sentiment', text)
raw = httr::GET(url)
content = rawToChar(raw$content)
content


```


## 1.2 Content classification using IAB-Taxonomy

Here we use the IAB_Taxonomy, which is available in uClassify API services:

```{r pressure2}
library(tidyverse)

uClassifyURL = function(key, classifierName, text) {
    text = gsub(" ", "+", text)
    url = sprintf("https://api.uclassify.com/v1/uClassify/%s/classify/?readKey=%s&text=%s", classifierName, key, text)
    return(url)
  }

  
text = "I'm positive that my job search will lead me to the job that I truly deserve."
url = uClassifyURL('iGwAytFWYvvZ', 'IAB-Taxonomy-V2', text)
raw = httr::GET(url)
content = rawToChar(raw$content)


data = rjson::fromJSON(content)
data[199]
```




# 2. O*NET Occupational Information
The Occupational Information Network (**O*NET**) is a free online database that contains hundreds of job definitions to help students, job seekers, businesses and workforce development professionals to understand today's world of work in the United States. Here I demo how you can get information about an occupation from ONET APIs. We use Bioscientist as an occupation, and get updated information about this occupation from O*NET:


```{r pressure4}
library(ONETr)
setCreds("uts_edu_au","2393xyk")
#Bioscientist: 15-2041.01
Bioscientist <- socSearch("15-2041.01")

skills <- skills(Bioscientist)
skills$name
skills$description

abilities <- abilities(Bioscientist)
abilities$name
abilities$description

knowledge <- knowledge(Bioscientist)
knowledge$name
knowledge$description

tasks <- tasks(Bioscientist)
tasks$statement

education(Bioscientist)
interests(Bioscientist)
jobTitles(Bioscientist)

technology <- technology(Bioscientist)
technology$title.text
technology$example.text

tools <- tools(Bioscientist)
tools$title.text
tools$example

workActivities <- workActivities(Bioscientist)
workActivities$name
workActivities$description

```




